Growth Resilience

### 2017-06-22 analysis/analysis_resilience_bai.Rmd
update plot interactions

dodge <- position_dodge(width = 0.3)
micolor <- '#455883'
```

```{r}
plot_ms <- means_site %>%  
  ggplot(aes(x=site, y=lsmean)) + 
  geom_errorbar(aes(ymin=lsmean - SE, ymax=lsmean + SE), 
                color=micolor, size=.5, width=.15, position = dodge) +
  geom_point(colour=micolor, 
             size=3, position = dodge) +
  theme_bw() + xlab('') + ylab('') + 
  facet_wrap(~var, scales='free_y', ncol = 1) +
  geom_text(aes(y=lsmean, label=letras), nudge_x = 0.15) +
  theme(strip.background = element_rect(colour = "black", fill = "white"))
```

```{r}
plot_md <- means_disturb %>%  
  ggplot(aes(x=disturb_year, y=lsmean)) + 
  geom_errorbar(aes(ymin=lsmean - SE, ymax=lsmean + SE), 
                color=micolor, size=.5, width=.15, position = dodge) +
  geom_point(colour=micolor, 
             size=3, position = dodge) +
  theme_bw() + xlab('') + ylab('') + 
  facet_wrap(~var, scales='free_y', ncol = 1) +
  geom_text(aes(y=lsmean, label=letras), nudge_x = 0.15) +
  theme(strip.background = element_rect(colour = "black", fill = "white"))
```

```{r}
plot_mds <- means_distub_site %>%  
  ggplot(aes(x=site, y=lsmean, group=disturb_year, colour=disturb_year)) + 
  geom_errorbar(aes(ymin=lsmean - SE, ymax=lsmean + SE), 
                size=.5, width=.15) + 
  geom_point(aes(shape=disturb_year), size=3) + 
  geom_line() +
  theme_bw() + xlab('') + ylab('') + 
  facet_wrap(~var, scales='free_y', ncol = 1) +
  geom_text(aes(y=lsmean+SE, label=letras), nudge_x = 0.15)+
  theme(strip.background = element_rect(colour = "black", fill = "white"),
        legend.position = c(0.8, 0.93),
        legend.background = element_blank()) +
  scale_colour_manual(values = c(micolor, "red"))

@@

```{r}
pdf(paste0(di, 'out/fig/resilience/interaction_plots.pdf'), width=9, height = 9)
grid.arrange(plot_md, plot_ms, plot_mds, ncol=3)
dev.off()
```

>>>>

@@

```{r}
dodge <- position_dodge(width = 0.3)
micolor <- '#455883'
mierrorbarSE <- aes(ymin=lsmean - SE, ymax=lsmean + SE)
mierrorbar <- aes(ymin=lower.CL, ymax=upper.CL)
```

```{r}
plot_ms <- means_site %>%  
  ggplot(aes(x=site, y=lsmean)) + 
  geom_point(colour=micolor, 
             size=3, position = dodge) +
  theme_bw() + xlab('') + ylab('') + 
  facet_wrap(~var, scales='free_y', ncol = 1) +
  geom_text(aes(y=lsmean, label=letras), nudge_x = 0.15) +
  theme(strip.background = element_rect(colour = "black", fill = "white"))

plot_msSE <- plot_ms + geom_errorbar(mierrorbarSE,color=micolor, 
                                     size=.5, width=.15, position = dodge)

plot_msCI <- plot_ms + geom_errorbar(mierrorbar,color=micolor, 
                                     size=.5, width=.15, position = dodge)
```

```{r}
plot_md <- means_disturb %>%  
  ggplot(aes(x=disturb_year, y=lsmean)) + 
  geom_point(colour=micolor, 
             size=3, position = dodge) +
  theme_bw() + xlab('') + ylab('') + 
  facet_wrap(~var, scales='free_y', ncol = 1) +
  geom_text(aes(y=lsmean, label=letras), nudge_x = 0.15) +
  theme(strip.background = element_rect(colour = "black", fill = "white"))

plot_mdSE <- plot_md + geom_errorbar(mierrorbarSE,color=micolor, 
                                     size=.5, width=.15, position = dodge)

plot_mdCI <- plot_md + geom_errorbar(mierrorbar,color=micolor, 
                                     size=.5, width=.15, position = dodge)
```

```{r}
plot_mds <- means_distub_site %>%  
  ggplot(aes(x=site, y=lsmean, group=disturb_year, colour=disturb_year)) + 
  geom_point(aes(shape=disturb_year), size=3) + 
  geom_line() +
  theme_bw() + xlab('') + ylab('') + 
  facet_wrap(~var, scales='free_y', ncol = 1) +
  geom_text(aes(y=lsmean+SE, label=letras), nudge_x = 0.15)+
  theme(strip.background = element_rect(colour = "black", fill = "white"),
        legend.position = c(0.8, 0.93),
        legend.background = element_blank()) +
  scale_colour_manual(values = c(micolor, "red"))

plot_mdsSE <- plot_mds + geom_errorbar(mierrorbarSE, size=.5, width=.15)
plot_mdsCI <- plot_mds + geom_errorbar(mierrorbar, size=.5, width=.15)
```

```{r}
pdf(paste0(di, 'out/fig/resilience/interaction_plotsSE.pdf'), width=9, height = 9)
grid.arrange(plot_mdSE, plot_msSE, plot_mdsSE, ncol=3)
dev.off()

pdf(paste0(di, 'out/fig/resilience/interaction_plotsCI.pdf'), width=9, height = 9)
grid.arrange(plot_mdCI, plot_msCI, plot_mdsCI, ncol=3)
dev.off()
